Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-10 prop_letter.tex
prop_letter.tex Updating footnotes according to the meeting...

It asserts that there exists no function~$v$~\footnote{\yutsung{Kochen-Specker's original paper~\cite{kochenspecker1967}
used $\mathcal{E}$, but the Stanford Encyclopedia of Philosophy~\cite{Held2016}
used $v$. I think it is less confusion to use $v$ here.}} assigning definite values to all observables such that for any sequence
of commuting observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
 &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).
\end{eqnarray}
\end{subequations}Suppose that there is a function~$v$ satisfying
these two properties, it must send an observable to its eigenvalues
so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
\end{aligned}
\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{aligned}v(\mathbb{1} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\mathbb{1}) & v(\sigma_{z} & \otimes\sigma_{z})\\
v(\sigma_{x} & \otimes\mathbb{1}) & v(\mathbb{1} & \otimes\sigma_{x}) & v(\sigma_{x} & \otimes\sigma_{x})\\
v(\sigma_{x} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\sigma_{x}) & v(\sigma_{y} & \otimes\sigma_{y})
\end{aligned}
\label{eq:MerminSquare-values}
\end{equation}
satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).

@@

To understand the relation between IVPMs and states, it is instructive
to consider the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis.}
\end{cases}
\end{equation}
$\mu_{0}$ is not induced by the Born rule as a whole, but is consistent
with the Born rule on $\events_{0}$ and some other proper sub-event
spaces. The similar phenomena happens for IVPMs as well. Formally,
given a quantum IVPM~$\bar{\mu}$, the \emph{core} relative to a
sub-event space~$\events'\subseteq\events$ is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
While this change might make it easier to explain the core of quantum
IVPMs, should we explain the meaning of the Born rule for classical
probability measures?}}
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
The core of an interval-valued probability measure is the set of states
it approximates. For example, $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. The 2-dimensional measure~$\mu_{0}$
can be understood by core as well. Consider the IVPM~$\bar{\mu}_{0}=\iota_{\infty}\circ\mu_{0}$
whose cores are\begin{subequations}
\begin{eqnarray}
\mathrm{core}\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
\mathrm{core}\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
\mathrm{core}\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
\end{eqnarray}
\end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
That is, $\bar{\mu}_{0}$ approximates $\proj{\ps}$ if we are only
allowed to use $\events_{0}$ during the measurement, and approximates
$\proj{0}$ if $\events_{1}$ are the only allowed ones. Since $\bar{\mu}_{0}$
approximates different states on different sub-event space, it intuitively
approximates nothing if every projector is allowed.

>>>>

It asserts that there exists no function~$v$ assigning definite
values to all observables such that for any sequence of commuting
observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
 &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).
\end{eqnarray}
\end{subequations}Suppose that there is a function~$v$ satisfying
these two properties, it must send an observable to its eigenvalues
so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
\end{aligned}
\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{aligned}v(\mathbb{1} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\mathbb{1}) & v(\sigma_{z} & \otimes\sigma_{z})\\
v(\sigma_{x} & \otimes\mathbb{1}) & v(\mathbb{1} & \otimes\sigma_{x}) & v(\sigma_{x} & \otimes\sigma_{x})\\
v(\sigma_{x} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\sigma_{x}) & v(\sigma_{y} & \otimes\sigma_{y})
\end{aligned}
\label{eq:MerminSquare-values}
\end{equation}
satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).

@@

To understand the relation between IVPMs and states, it is instructive
to consider the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis.}
\end{cases}
\end{equation}
$\mu_{0}$ is not induced by the Born rule as a whole, but is consistent
with the Born rule on $\events_{0}$ and some other proper sub-event
spaces. The similar phenomena happens for IVPMs as well. Formally,
given a quantum IVPM~$\bar{\mu}$, the \emph{core} relative to a
sub-event space~$\events'\subseteq\events$ is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
While this change might make it easier to explain the core of quantum
IVPMs, should we explain the meaning of the Born rule for classical
probability measures? Check this definition in the classical setting,
like commuting observables or product states... etc.}}
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
The core of an interval-valued probability measure is the set of states
it approximates. For example, $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. The 2-dimensional measure~$\mu_{0}$
can be understood by core as well. Consider the IVPM~$\bar{\mu}_{0}=\iota_{\infty}\circ\mu_{0}$
whose cores are\begin{subequations}
\begin{eqnarray}
\mathrm{core}\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
\mathrm{core}\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
\mathrm{core}\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
\end{eqnarray}
\end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
That is, $\bar{\mu}_{0}$ approximates $\proj{\ps}$ if we are only
allowed to use $\events_{0}$ during the measurement, and approximates
$\proj{0}$ if $\events_{1}$ are the only allowed ones. Since $\bar{\mu}_{0}$
approximates different states on different sub-event space, it intuitively
approximates nothing if every projector is allowed.
